---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{eco2concert.plattform}`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Installation

### Working with **golem** in VS Code  
Although **golem** is designed for RStudio, it’s all standard R code and a familiar folder structure so VS Code works just fine.  
> **Tip:** Install the “R” extension (and any recommended add-ons) when prompted by VS Code.

To get started, run in your R console or VS Code R terminal:

```{r, eval=FALSE}
install.packages("golem")
library(golem)

golem::install_dev_deps()
```
You may be prompted to install some dependencies. I would just install them all.


## Run

You can launch the application by running:

```{r, eval = FALSE}
eco2concert.plattform::run_app()
```

## About

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```

Here are the tests results and package coverage:

```{r, error = TRUE}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("eco2concert.plattform")
```

```{r, error = TRUE}
covr::package_coverage()
```
